---
output:
  html_document:
    keep_md: yes
    number_sections: true
    toc: true
    toc_float: true
params:
  summary_table_file: summary_table.tsv
  IGV_snapshot_dir: IGV_snapshots
  analysis_ID: NA
  sample_ID: NA
  barcode_ID: NA
---
<!-- Setup the R code to be used in R Markdown generation throughout the report -->
```{r setup, include=FALSE}
# {.tabset} # .tabset-fade .tabset-pills
knitr::opts_chunk$set(echo = FALSE)

library("knitr")

mycat <- function(text){
    # function for formatting text in the report
    cat(gsub(pattern = "\n", replacement = "  \n", x = text))
}

file_scan <- function(my_file){
    # function for reading info from a text file
    file_contents <- scan(my_file, what="", sep="\n")
    return(file_contents)
}

get_file_content <- function(my_file){
    # function to return file contents or NA if file doesn't exit
    file_contents <- "NA"
    if (file.exists(my_file)) {
        if (! identical(file_scan(my_file), character(0))) {
            file_contents <- file_scan(my_file)
        }
    }
    return(file_contents)
}

reindex_rownames <- function(df){
    # reindex the row names after subsetting
    if(nrow(df) > 0) rownames(df) <- seq(nrow(df))
    return(df)
}

print_barcodes_table <- function(df, cols_to_print, caption){
    print(kable(df[cols_to_print], caption = caption, row.names = TRUE))
}

print_variant_table <- function(df, cols_to_print){
    # print the variant table into the report
    if(nrow(df) > 0) print(kable(df[cols_to_print], row.names = TRUE))
}

print_SC_variant_table <- function(df, cols_to_print){
    # special conditions for the SC variant table printing
    if(nrow(df) > 0){
        mycat('\n\n## SC Sample\n\n')
        mycat('\n\nThe following variants were detected in the SC control sample:\n\n')
        print_variant_table(df, cols_to_print)
    }
}

```


```{r get_report_params, echo = FALSE, include = FALSE, eval=TRUE}
# get the items for the report
summary_table_file <- params$summary_table_file
IGV_snapshot_dir <- params$IGV_snapshot_dir

analysis_ID <- get_file_content("analysis_ID.txt")
```

```{r load_barcodes_tables, echo = FALSE, include = FALSE, eval=TRUE}
# columns to include in the report output
sample_barcode_cols <- c("Sample.Name", "Barcode")
sample_barcodes_file <- "sample_barcode_IDs.tsv"
sample_barcodes_df <- read.delim(sample_barcodes_file, header = TRUE, sep = '\t') # , check.names = FALSE
# order by barcode
sample_barcodes_df <- sample_barcodes_df[order(sample_barcodes_df[["Barcode"]]), ]
sample_barcodes_df <- reindex_rownames(sample_barcodes_df)

run_ID <- unique(as.character(sample_barcodes_df[["Run.Name"]]))
```

```{r load_variant_tables, echo = FALSE, include = FALSE, eval=TRUE}
# colnames to print in the variant summary tables
summary_cols <- c("Gene", "Coding", "Amino.Acid.Change","Frequency", "Review", "Sample.Name", "Barcode")

# ID's of the SC control samples; filter these from the primary table
SC_control_sampleIDs <- c("SC", "Sc")

# load variant summary table from file
summary_df <- read.delim(summary_table_file, header = TRUE, sep = '\t')
# round off the Frequency value
summary_df[["Frequency"]] <- round(summary_df[["Frequency"]], 3)

# separate the SC and non-SC samples
non_sc_summary_df <- summary_df[ which(! summary_df[["Sample.Name"]] %in% SC_control_sampleIDs), ]
non_sc_summary_df <- reindex_rownames(non_sc_summary_df)

sc_summary_df <- summary_df[ which(summary_df[["Sample.Name"]] %in% SC_control_sampleIDs), ]
sc_summary_df <- reindex_rownames(sc_summary_df)
```
<!-- Start printing the report contents -->
<!-- Custom report header -->
<div class="fluid-row" id="header">
<h1 class="title toc-ignore">Gene Panel Analysis Report</h1>
<h4 class="author" style="display: inline; float: left;"><em>Stephen Kelly</em></h4>
<h4 class="date" style=" inline; float: right;"><em>`r format(Sys.time(), '%B %d, %Y')`</em></h4>
</div>
<br>
<hr class="section-rule">

<!-- Custom report CSS styling -->
<style>
/* custom line between sections */
.section-rule {
color: lightgray;
}

/* color the active TOC element purple */
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: indigo;
}

/*
#header h1 {
    color: purple; 
    border-bottom: 1px solid purple;
    padding-bottom: 15px;
}
*/

/* color the active pill buttons purple with white text */

.nav-pills > li.active > a, .nav-pills > li.active > a:focus {
color: white;
background-color: indigo;
}
/* color the inactive pill button text purple */

.nav-pills > li.active > a:hover {
background-color: indigo;
color:white;
}

.nav>li>a {
color: indigo;
background-color: lightgray;
}

</style>


# Analysis Information

Analysis ID:

<strong>`r analysis_ID`</strong>

Run ID:

<strong>`r run_ID`</strong>

```{r print_sample_barcodes_table, results='asis'}
print_barcodes_table(sample_barcodes_df, sample_barcode_cols, "Samples included in the analysis.")
```

# Variant Table {.tabset .tabset-pills}

## Non-SC Samples

The following variants are detected:

```{r print_non_SC_variant_table, echo = FALSE, results='asis', eval=TRUE}
print_variant_table(non_sc_summary_df, summary_cols)
```

```{r print_SC_variant_table, echo = FALSE, results='asis', eval=TRUE}
print_SC_variant_table(sc_summary_df, summary_cols)
```

# IGV Snapshots

```{r, results='asis'}
# get paths to the snapshots
IGV_snapshots <- grep(pattern = 'long.png', x = dir(path = IGV_snapshot_dir, pattern = "*.png", full.names = TRUE), value = TRUE, invert = TRUE)

# paths to the 'long' snapshots
IGV_long_snapshots <- dir(path = IGV_snapshot_dir, pattern = "*long.png", full.names = TRUE)

if(length(IGV_snapshots) > 0){
    # add filenames as item names
    IGV_snapshots <- setNames(object = IGV_snapshots, nm = basename(IGV_snapshots))

    # print each to a new section, parse the name for the section name
    for(i in seq_along(IGV_snapshots)){
        # parse section items
        snapshot_filepath <- IGV_snapshots[i]
        snapshot_name <- names(IGV_snapshots[i])
        snapshot_elements <- unlist(strsplit(x = snapshot_name, split = '.', fixed = TRUE))

        snapshot_elements <- setNames(object = snapshot_elements,
                                      nm = c("Analysis_ID", "Barcode", "Gene", "Chrom", "Pos", "Coding_c", "Coding_ID", "Extension"))

        coding_ID <- paste(snapshot_elements[["Coding_c"]],
                           snapshot_elements[["Coding_ID"]], sep = '.')

        section_heading <- paste(snapshot_elements[["Gene"]], coding_ID,
                                 snapshot_elements[["Barcode"]] ,sep = ' ')

        variant_ID <- gsub(x = snapshot_name, pattern = ".png", replacement = "")

        # get the entry for this variant from the original df
        variant_df <- subset(non_sc_summary_df,
                             subset=(Barcode == snapshot_elements[["Barcode"]] &
                                         Gene == snapshot_elements[["Gene"]] &
                                         Position == snapshot_elements[["Pos"]] &
                                         Chrom == snapshot_elements[["Chrom"]]))



        # check for a 'long' snapshot
        search_pattern <- gsub(pattern = '.png', replacement = '', x = names(snapshot_filepath))
        long_snapshot_file <- grep(pattern = search_pattern, x = IGV_long_snapshots, value = TRUE)

        if( ! identical(long_snapshot_file, character(0))) {
            # start printing the section
            mycat(paste0("## ", section_heading, " {.tabset .tabset-pills} \n\n"))
            mycat("### Short View \n\n")
            mycat("Variant ID:\n\n")
            mycat(paste0('`', variant_ID,'`\n\n'))
            print(kable(variant_df[summary_cols], row.names = FALSE))
            mycat(paste0("\n\n![](", snapshot_filepath, ") \n\n"))

            mycat("### Long View \n\n")
            mycat("Variant ID:\n\n")
            mycat(paste0('`', variant_ID,'`\n\n'))
            print(kable(variant_df[summary_cols], row.names = FALSE))
            mycat(paste0("\n\n![](", long_snapshot_file, ") \n\n"))

        } else{
            mycat(paste0("## ", section_heading, " {.tabset .tabset-pills} \n\n"))
            mycat("Variant ID:\n\n")
            mycat(paste0('`', variant_ID,'`\n\n'))
            print(kable(variant_df[summary_cols], row.names = FALSE))
            mycat(paste0("\n\n![](", snapshot_filepath, ") \n\n"))
        }


    }
}

```


# System Information {.tabset .tabset-pills}

## Hide

## Show

```{r}
# system info
system("uname -srv", intern = TRUE)

# dir
system('pwd',intern=T)

# repo info
system('git remote -v')
system('printf "%s\t%s" "$(git rev-parse --abbrev-ref HEAD)" "$(git rev-parse HEAD)"')

# date time
system("date", intern = TRUE)

# R system info, packages, etc
sessionInfo()

# save current session
save.image(file="overview_report_data.Rdata",compress = TRUE)
```
